Proving Logical Atomicity using Lock Invariants\thanks{Supported by the National Science Foundation via grant \#1811894.}

### 2022-05-18 concurrency/ASL 2022/Verification of Concurrent Binary Search Tree.tex
Adjust the layout of one formula

The $\treerep$ predicate describes the conditions under which an abstract map $m$ is implemented by the ghost state of a tree. Intuitively, we should be able to gather the per-node ghost states into an abstract tree $t$ that implements the map $m$, in that each key-value pair in $m$ appears in one of the nodes of $t$. We formalize this by first defining the collection of per-node ghost state fragments needed to form an abstract tree:
\[\begin{array}{r l}
\mathsf{public}&\mathsf{\_halves}(t, g, (i, j)) \triangleq \mathsf{match}\ t\ \mathsf{with}\\
& |\ \mathsf{Leaf} \Rightarrow \publichalf{g}{(i, j), \mathsf{None}}\\
& |\ \mathsf{Node}\ (k, v, t_l, g_l, t_r, g_r) \Rightarrow \publichalf{g}{(i, j), \mathsf{Some}\ (k, v, g_l, g_r)}\ * \\&\qquad\mathsf{public\_halves}(t_l, g_l, (i, k)) * \mathsf{public\_halves}(t_r, g_r, (k, j))
\end{array}\]
We recursively walk through the tree, starting from a node $g$ with range $(i, j)$, and collect the $\mathsf{node\_ghost}$ assertions of each node into a single assertion. We compute the range of each node's children as described above: if the key in the current node is $k$, then the left child has range $(i, k)$ and the right child has range $(k, j)$.

>>>>

The $\treerep$ predicate describes the conditions under which an abstract map $m$ is implemented by the ghost state of a tree. Intuitively, we should be able to gather the per-node ghost states into an abstract tree $t$ that implements the map $m$, in that each key-value pair in $m$ appears in one of the nodes of $t$. We formalize this by first defining the collection of per-node ghost state fragments needed to form an abstract tree:
\[\begin{array}{r l}
& \mathsf{public\_halves}(t, g, (i, j)) \triangleq \mathsf{match}\ t\ \mathsf{with}\\
& \;\qquad |\ \mathsf{Leaf} \Rightarrow \publichalf{g}{(i, j), \mathsf{None}}\\
& \;\qquad |\ \mathsf{Node}\ (k, v, t_l, g_l, t_r, g_r) \Rightarrow \publichalf{g}{(i, j), \mathsf{Some}\ (k, v, g_l, g_r)}\ * \\
& \;\qquad \qquad\mathsf{public\_halves}(t_l, g_l, (i, k)) * \mathsf{public\_halves}(t_r, g_r, (k, j))
\end{array}\]
We recursively walk through the tree, starting from a node $g$ with range $(i, j)$, and collect the $\mathsf{node\_ghost}$ assertions of each node into a single assertion. We compute the range of each node's children as described above: if the key in the current node is $k$, then the left child has range $(i, k)$ and the right child has range $(k, j)$.
